Molecular alignment at graphene surface determines tansport properties of graphene transistors

### 2020-04-03 manuscript.tex
Update manuscript.tex
Morphology

Morphology of the PDI8-CN2 layer on a single layer graphene is shown in Figure \ref{fig:1}a, where we show a LxW $\mu m^2$ AFM topography scan of the area of the sample. The topography of graphene is flat and characterized by few linear steps/folds in the upper left part of the image. In the image brighter tones represent higher elevations, and the dark irregular patches represent depressions in the otherwise continuous PDI8-CN2 layer. Figure \ref{fig:1}b  shows a normalized distribution of the height data obtained from the image shown in Figure \ref{fig:1}a). The data (dark points) were fitted with two Gaussian functions (green curves) that yield a composite fit (red curve) for the whole range of data. The lower peak in the distribution corresponds to the height data from the depressions, and the higher peak corresponds to the data of the layer. The origin of the height scale has been shifted to the position of the centroid describing the depressions, so that the height difference between the centroids of the two Gaussian functions reads as 0.66$\pm$xx nm, where the error is the average of the full-width at half maximum of the two Gaussian functions.  The thickness of the PDI8-CN2 layer is therefore 0.664$\pm$ xx nm.\textbf{ *Continue*}
\begin{figure}[htb]
  \centering
        \includegraphics[width=0.9\textwidth]{./Figures/fig1}
  \caption{a) The non-contact topography map of the PDI8-CN2 layer on a single-layer graphene. The growth time was 1 minute. Brighter tones represent higher elevations. The straight lines in the upper left portion of the image are folds in graphene. Dark irregularly-shaped patches are depressions in an otherwise continuous layer of PDI8-CN2.  b) The height distribution of the image shown in Figure 1a). The histogram has been normalized to the highest value in the image. The black dots represent the data, the green curves are Gaussian functions used to fit the data. The composite fit is represented by the red curve. The leftmost peak corresponds to the depressions in the complete layer represented by the highest peak.}
  \label{fig:1}
\end{figure}

@@

The observed layer thickness in our case is consistent with PDIF8-CN2 molecules lying flat on the graphene substrate, since the a-axis of the PDI8-CN2 unit cell, is 0.5 nm \textbf{[Ref]}. We also note, that no second layer nucleation is observed although the coverage of the first monolayer is 70 \%. This is consistent with the results from Ref. \onlinecite{liscio-2013}, who observed the onset of nucleation of the second layer upon completion of 95 \% coverage of the first. The rms roughness of our layers was consistently found to be XXX \%. As the exposure to the source materials increased from 1 minute to 3 minutes. The layer morphology changes as illustrated in Figure \ref{fig:2}. Figure \ref{fig:2}a is a  5$\times$5 $\mu$m topography map and shows two broad regions. The brighter region on the left of the image diagonal corresponds to single-layer graphene, the region on the right is SiO$_{2}$ substrate. 
\begin{figure}[htb]
  \centering
   \includegraphics[width=0.9\textwidth]{./Figures/fig2}
  \caption{a) $5\times5 \mu$m$^{2}$ non-contact topography map of a PDI8-CN2 layer on a single-layer graphene (leftmost region of the image) and on SiO$_{2}$ (rightmost region of the image). The growth time was 3 minutes. Brighter tones represent higher elevations. b) The height distribution of the image shown in Figure 2a) obtained from the height data of graphene region only. The histogram has been normalized to the highest value in the image. The black dots represent the data, the green curves are Gaussian functions used to fit the data. The composite fit is represented by the red curve.  The leftmost peak corresponds to the depressions in the complete layer, which is represented by the highest peak. The lowest peak in the model corresponds to the few islands nucleating on the second layer.}
  \label{fig:2}
\end{figure}

The histogram shown in Figure \ref{fig:2}b shows three Gaussian peaks (green curves) and a composite fit (red curves) and was obtained by analysis of the part of the image shown in Figure \ref{fig:2}a pertinent to graphene. The origin of the height scale was shifted to the centroid leftmost peak comprising data from the depressions in the layer, which contributes the height data of the highest peak. The rightmost peak at the highest elevations corresponds to few islands that nucleated on top of the second layer. The height separation between the leftmost and the central peak amounts to 1.75 XX nm. This value is consistent with the upright orientation of the molecules in the layers. We note that the morphology of the PDI8-CN2 layer on SiO$_{2}$ is somewhat different in the sense that the density of the third-layer islands  of the same height (1.75 nm) as on graphene is observed here. This is consistent to the data by Liscio et al. for the growth of PDI8-CN2 on SiO$_{2}$ at room temperature, where an increased heterogeneity in growth mode, i.e. flat-lying and upright oriented molecules within the same layer was reported. The likelihood of flat-lying molecules on graphene is conceivable also from the energetic considerations. The interaction energy between graphene and PDI-CN2 (neglecting the polymer part) can be calculated based on the work of Bj\"{o}k et al.\cite{bjork-2010} and amounts to ~1.6 eV, which is between, for example para-hexaphenyl (~2.6 eV) and pentacene (~1.3 eV), both of which were found to form ordered islands of flat-lying molecules on single-layer graphene, under suitable circumstances\cite{kratzer-2016}.

Differences in the growth mode of PDI8-CN2 on graphene and on SiO$_{2}$ are several. Firstly, we note the absence of the disorder during growth of the first monolayer, which may originate from the dipole layer at the graphene/SiO$_{2}$ interface, which was shown to alter the graphene surface energy and therefore the interaction between graphene and PDI8-CN2 molecules\cite{sabio-2008}\cite{chhikara-2014}. This results in vast majority of molecules to lay flat on graphene surface.\cite{kratzer-2016}  Secondly, the rate of nucleation of the third layer of PDI8-CN2 on graphene is strongly reduced to that of PDI8-CN2 on SiO$_{2}$, which may be a consequence of the improved molecular dynamics of PDI8-CN2 molecules on a complete first monolayer comprising only flat-lying molecules.   From this analysis of the growth mode we can therefore conclude that PDI8-CN2 grows in a layer-by-layer mode at least for the first two monolayers. It forms a continuous first monolayer of flat-lying molecules on graphene, followed by another layer of upright oriented molecules.

>>>>

Morphology of the PDI8-CN2 layer on a single layer graphene is shown in Figure \ref{fig:1}a, where we show a 20 x 20 $\mu m^2$ AFM topography scan of the area of the sample. The topography of graphene is flat and characterized by few linear steps/folds in the upper left part of the image. In the image brighter tones represent higher elevations, and the dark irregular patches represent depressions in the otherwise continuous PDI8-CN2 layer. Figure \ref{fig:1}b  shows a normalized distribution of the height data obtained from the image shown in Figure \ref{fig:1}a). The data (dark points) were fitted with two Gaussian functions (green curves) that yield a composite fit (red curve) for the whole range of data. The lower peak in the distribution corresponds to the height data from the depressions, and the higher peak corresponds to the data of the layer. The origin of the height scale has been shifted to the position of the centroid describing the depressions, so that the height difference between the centroids of the two Gaussian functions reads as 0.6 $\pm$ 0.6 nm, where the error is the average of the full-width at half maximum of the two Gaussian functions.  The thickness of the PDI8-CN2 layer is therefore 0.6 $\pm$ 0.6 nm.\textbf{ *Continue*   what should i add? }
\begin{figure}[htb]
  \centering
        \includegraphics[width=0.9\textwidth]{./Figures/fig1}
  \caption{a) The non-contact topography map of the PDI8-CN2 layer on a single-layer graphene. The growth time was 1 minute. Brighter tones represent higher elevations. The straight lines in the upper left portion of the image are folds in graphene. Dark irregularly-shaped patches are depressions in an otherwise continuous layer of PDI8-CN2.  b) The height distribution of the image shown in Figure 1a). The histogram has been normalized to the highest value in the image. The black dots represent the data, the green curves are Gaussian functions used to fit the data. The composite fit is represented by the red curve. The leftmost peak corresponds to the depressions in the complete layer represented by the highest peak.}
  \label{fig:1}
\end{figure}

@@

The observed layer thickness in our case is consistent with PDI8-CN2 molecules lying flat on the graphene substrate, since the a-axis of the PDI8-CN2 unit cell, is 0.5 nm \cite{liscio-2012}. We also note, that no second layer nucleation is observed although the coverage of the first monolayer is less than 70 \%. This is consistent with the results from Ref. \onlinecite{liscio-2013}, who observed the onset of nucleation of the second layer upon completion of 95 \% coverage of the first. The rms roughness of our layers was consistently found to be 0.5 nm. As the exposure to the source materials increased from 1 minute to 3 minutes. The layer morphology changes as illustrated in Figure \ref{fig:2}. Figure \ref{fig:2}a is a  3$\times$3 $\mu$m topography map and shows two broad regions. The brighter region on the left of the image diagonal corresponds to single-layer graphene, the region on the right is SiO$_{2}$ substrate. 
\begin{figure}[htb]
  \centering
   \includegraphics[width=0.9\textwidth]{./Figures/fig2}
  \caption{a) $3\times3 \mu$m$^{2}$ non-contact topography map of a PDI8-CN2 layer on a single-layer graphene (leftmost region of the image) and on SiO$_{2}$ (rightmost region of the image). The growth time was 3 minutes. Brighter tones represent higher elevations. b) The height distribution of the image shown in Figure 2a) obtained from the height data of graphene region only. The histogram has been normalized to the highest value in the image. The black dots represent the data, the green curves are Gaussian functions used to fit the data. The composite fit is represented by the red curve.  The leftmost peak corresponds to the depressions in the complete layer, which is represented by the highest peak. The lowest peak in the model corresponds to the few islands nucleating on the second layer.}
  \label{fig:2}
\end{figure}

The histogram shown in Figure \ref{fig:2}b shows three Gaussian peaks (green curves) and a composite fit (red curves) and was obtained by analysis of the part of the image shown in Figure \ref{fig:2}a pertinent to graphene. The origin of the height scale was shifted to the centroid leftmost peak comprising data from the depressions in the layer, which contributes the height data of the highest peak. The rightmost peak at the highest elevations corresponds to few islands that nucleated on top of the second layer. The height separation between the leftmost and the central peak amounts to 1.75 $\pm$ 1 nm. This value is consistent with the upright orientation of the molecules in the layers. We note that the morphology of the PDI8-CN2 layer on SiO$_{2}$ is somewhat different in the sense that the density of the third-layer islands  of the same height (1.72 $\pm$ 0.8 nm ) as on graphene is observed here. This is consistent to the data by Liscio et al. for the growth of PDI8-CN2 on SiO$_{2}$ at room temperature, where an increased heterogeneity in growth mode, i.e. flat-lying and upright oriented molecules within the same layer was reported. The likelihood of flat-lying molecules on graphene is conceivable also from the energetic considerations. The interaction energy between graphene and PDI-CN2 (neglecting the polymer part) can be calculated based on the work of Bj\"{o}k et al.\cite{bjork-2010} and amounts to ~1.6 eV, which is between, for example para-hexaphenyl (~2.6 eV) and pentacene (~1.3 eV), both of which were found to form ordered islands of flat-lying molecules on single-layer graphene, under suitable circumstances\cite{kratzer-2016}.

Differences in the growth mode of PDI8-CN2 on graphene and on SiO$_{2}$ are several. Firstly, we note the absence of the disorder during growth of the first monolayer, which may originate from the dipole layer at the graphene/SiO$_{2}$ interface, which was shown to alter the graphene surface energy and therefore the interaction between graphene and PDI8-CN2 molecules\cite{sabio-2008,chhikara-2014}. This results in vast majority of molecules to lay flat on graphene surface\cite{kratzer-2016}.  Secondly, the rate of nucleation of the third layer of PDI8-CN2 on graphene is strongly reduced to that of PDI8-CN2 on SiO$_{2}$, which may be a consequence of the improved molecular dynamics of PDI8-CN2 molecules on a complete first monolayer comprising only flat-lying molecules.   From this analysis of the growth mode we can therefore conclude that PDI8-CN2 grows in a layer-by-layer mode at least for the first two monolayers. It forms a continuous first monolayer of flat-lying molecules on graphene, followed by another layer of upright oriented molecules.
